%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size



\input{structure.tex} % Include the file specifying document layout
\usepackage{multicol}
\usepackage{nopageno}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Pip Turner} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Home Address} \> 145 Murdock Road,\\ % Address line 1
\> Birmingham, B21 9JR \\ % Address line 2
{\bf Term Address} \> Frondewi, Stanley Road,\\ % Address line 1
\> Penglais, Aberystwyth, SY23 1LS \\ % Address line 2


{\bf Mobile Phone} \> 07976549682 \\ % Mobile phone
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
%{\bf Home Phone} \> +0 (000) 111 1111 \\ % Home phone


{\bf GitHub} \> \href{www.github.com/dwarph}{github.com/dwarph}\\ % Website
{\bf LinkedIn} \> \href{https://www.linkedin.com/in/pip-turner97}{/pip-turner97}\\ % Website
{\bf Website} \> \href{pipturner.co.uk}{pipturner.co.uk}\\ % Website
{\bf Email} \> \href{mailto:pipturner@outlook.com}{pipturner@outlook.com} \\ % Email address

\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}
I am a programmer, game developer and writer, with over four years of programming experience, \\currently in my final year of BSc Computer Science at Aberystwyth University. I am reliable, self motivated and a good team member. I am looking for a role upon graduation within a company that can actively push me to learn and expand my current skill set, as well as giving me a great start to my career.

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

% \textbf{Programming Languages:}
% {
% \textit{Java, C\#, C, C++, Javascript} \\
% }

% \textbf{Markup Languages:}
% {
% \textit{HTML5, CSS, \LaTeX}\\
% }



\textbf{Programming Languages:} \textit{Java, C\#, C, C++ (inc. OpenGL), Javascript (Three.js \& P5), SQLite, PostgreSQL} \\ 

\textbf{Markup Languages:}\textit{ HTML5, CSS, \LaTeX} \\ 

\textbf{Software:} \textit{Windows, OSX, Linux, Unity 5, Blender, Git, SVN, Bitbucket \& Github}  \\

\textbf{Other:} \textit{Agile - Scrum, XP, TDD}\\ 

\textbf{Soft Skills} \newline
{}
\textit{Creativity, Leadership, Organisation, People Skills, Public Speaking, Reliability, Teamwork}\\
I volunteered as a youth group leader, which equipped me with valuable leadership and teamwork skills. I attended a drama group for 10 years, providing me with excellent communication skills. I was part of Aberystwyth's Christian Union committee - I organised two Bible study groups a week, trained leaders and advertised the study. This role helped me to develop my organisational, leadership and presentation skills.


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education \& Qualifications}

\tabbedblock{
\bf{2015-2018} \>  BSc (Hons) Computer Science (First Class) - \href{http://www.aber.ac.uk/}{Aberystwyth University} \\[5pt]

\>Achieved a Merit Award in the Aberystwyth Scholarship examination}
\begin{table}[h!]
\centering

\begin{tabular}{ll}
\textbf{Examples of Modules and Grades:} 						    &   \\
                                            						&   \\
\textit{Applied Graphics (94\%)}									& \textit{Computer Graphics and Games (79\%)} \\
\textit{Major Project (81\%)} 								        & \textit{Agile Methodologies (76\%)} \\
\textit{Artificial Intelligence (81\%)}                             & \textit{Software Engineering (75\%) } \\
\textit{Program Design, Data Structures \& Algorithms (79\%)}		& \textit{C and C++ Environments (75\%)}  \\

\end{tabular}
\end{table}


%------------------------------------------------

\tabbedblock{
\bf{2013-2015} \> A Levels - \href{http://www.handsworth.bham.sch.uk/}{Handsworth Grammar School, Birmingham}\\[5pt]
\>\+

\textit{Computing (B), English Literature (B), Mathematics (E)}\\
}

%------------------------------------------------

\tabbedblock{
\bf{2008-2013} \> GCSES - \href{http://www.handsworth.bham.sch.uk/}{Handsworth Grammar School, Birmingham}\\[5pt]
\>\+
\textit{13 GCSES}  A* - C (Including: Distinction ICT, A in Maths)  \\
}
\clearpage


\section{Projects}
To see my full portfolio, visit \href{www.pipturner.co.uk/portfolio}{pipturner.co.uk/portfolio}\\

\project {3D Procedurally Generated Nature Scene} {C++} {My Major Project, made as part of my degree. The project developed 3D procedurally generated natural scenes, concentrating on terrain and trees. Procedural generation algorithms were implemented from scratch using C++ and OpenGL.}

\project {QRTTNBPBYTROAYALID, An Infinite Runner} {Unity, C\#} 
{Quick, Run to The Next Battery Pack Before Your Torch Runs Out and You Are Left In Darkness!, is an infinite runner created for Ludum Dare \#39. I worked on the code and game design.} 

\project {3D "Temple of Doom" Scene} {JavaScript, Three.js}{3D Scene made for an assignment using Three.js. Each item was modelled using Three.js rather than using 3D Modelling software.}

\project {The Search For A Good Book} {Blender}
{A 1-2 minute animation made for an assignment using Blender. I used a low poly style to create something which looked good and allowed me to quickly create more content.}

\project {Buccaneer} {Java} {A Group Project Assignment in which we ported the Buccaneer Board Game to Java. I was in charge of the majority of the backend of the project, enabling it to follow the given requirements and triggering UI events.}



 
%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Previous Work}

\job
{2016-}{2018}
{Aberystwyth University, Penglais, Aberystwyth, Ceredigion, SY23 3BF}
{https://www.aber.ac.uk/en/}
{Demonstrator}
{Demonstrated for lower years in a variety of workshops including C, C++ and Java.} 

\job
{2015-}{2016}
{Handsworth Grammar School, Grove Ln, Handsworth, Birmingham, United Kingdom}
{http://www.handsworth.bham.sch.uk/}
{IT Technician}
{A yearly summer job. Projects I worked on included: \textit{Setting up a networked CCTV system, installing computers \& routers, server maintenance, organising and performing maintenance on switches, designing a reading journal, general IT support.}}

%-----------------------------------------------
%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\section{Voluntary Work}

\textbf{SpecialEffect (\textit{2015-Ongoing})}

I help on Special Effect's Stall at various events in the UK. Special Effect uses technology to enhance the quality of life of people with physical disabilities. This involves speaking with attendees about SpecialEffect, and running various demos.

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\textbf{Pip Writes Stuff  \textit{(medium.com/pip-writes-stuff) }} \
I have run a blog called Pip Writes Stuff since 2014. I write regularly for blog. I am particularly proud of a series called "Itching For More" which focuses on small, unknown alt games, and aims to provide a discussion surrounding them. Pip Writes Stuff has been featured twice in Rock Paper Shotgun's The Sunday Papers.\\

I play classical and electric guitar, violin and some piano. I cycle regularly and enjoy reading, both fiction and non fiction. Two books I’ve read recently are \textit{On The Road - Jack Kerouac} and \textit{Embed with Games - Cara Elison}, both of which were beautiful reads.
%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

\section{Referees}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Dr Andrew Starr\\ % Referee name
{\bf Company} \> Aberystwyth University \\ % Referee company
{\bf Position} \>  Teaching Fellow \\ % Referee job title 
{\bf Contact} \> \href{mailto:aos@aber.ac.uk}{aos@aber.ac.uk} % Referee contact information
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Mr Chris Eaton\\ % Referee name
{\bf Company} \> Handsworth Grammar School \\ % Referee company
{\bf Position} \> Technical Operations Manager \\ % Referee job title 
{\bf Contact} \> \href{mailto:ceaton@handsworth.bham.sch.uk}{ceaton@handsworth.bham.sch.uk} % Referee contact information
\end{tabbing}}
%----------------------------------------------------------------------------------------

\end{document}